---
title: "Example knir report in a targets pipeline"
author: "You"
date: "6/19/2020"
output: html_document
---

```{r setup, include=FALSE}
library(targets)
knitr::opts_chunk$set(echo = TRUE)
```

This `knitr` report demonstrates how to integrate literate programming with `targets`. First, open your `_targets.R` file an create two new targets: one to track this source file, and another to run the report itself. Both should be dynamic files. These targets are `report_rmd` and `report_html` below.

```{r, eval = FALSE}
tar_pipeline(
  # Define targets data and analysis somewhere in tar_pipeline().
  tar_target(
    report_rmd,
    # Tidy eval with !! is key, and the tidy_eval argument needs to be TRUE.
    !!tar_knitr("example_knitr_report.Rmd"),
    # tar_knitr() returns a path, and we want to track the file itself,
    # so we need this target to be a dynamic file:
    format = "file"
  ),
  tar_target(
    report_html,
    # Use the symbol report_rmd below to tell tar_make() that
    # report_render depends on report_rmd.
    # rmarkdown::render() returns the path to the output file,
    # which is exactly what we need for dynamic files.
    rmarkdown::render(report_rmd, quiet = TRUE),
    # This time, we track the HTML output as a dynamic file:
    format = "file"
  )
)
```

Now, let's imagine this report depends on other targets called `data` and `analysis`. To account for these dependencies, we need calls to `tar_read()` or `tar_load()` to reference them explicitly. Examples:

```{r}
tar_load(data)
```

```{r}
plot(tar_read(analysis))
```

Because `!!tar_knitr()` is part of the pipeline, `targets` automatically looks for `tar_load()` and `tar_read()` and detects targets `data` and `analysis` as dependencies. That means the report automatically reruns if the upstream dependencies change. And as an added bonus, you can run this report on its own as long as your current working directory has a `_targets` data store with the return values of these targets.

The code analysis tries to be intelligent, so `tar_load()` and `tar_read()` can appear in various places.

```{r}
f <- function() {
  targets::tar_read(name = data2)
}
```

However, the dependencies are always detected using static code analysis, which means `tidyselect` syntax like `tar_load(starts_with("data"))` will not work. `targets` requires you to write the literal symbol name of every target you want the report to depend on.

```{r}
tar_load()
```

```{r}
not
a
target
```
